\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}

\name{Ju Lin}
\address{ \href{https://github.com/soasme }{GitHub - @soasme} \\ \href{https://enqueuezero.com}{blog - enqueuezero.com}}
\address{ +64~$\cdot$~027~$\cdot$~545~$\cdot$~3988 \\ soasme@gmail.com}

\def\nameskip{\bigskip}
\def\sectionskip{\medskip}

\begin{document}

  \begin{rSection}{Summary}
    { {\bf Ju Lin } has a wide knowledge of DevOps, Web Programming, and System Administration. He is an expert in Python Programming, Operating System, and Kubernetes. He likes provisioning cloud resources by Infrastructure as Code. He is a passionate learner with endless curiosity and enjoys jumping out of the comfort zone. }
  \end{rSection}

  \begin{rSection}{Experience}

    \begin{rSubsection}{Workday}{ Mar 2017 - }{Senior DevOps Engineer}{Auckland, New Zealand}
    \item Developed and maintained a statuspage-like API and command line tools. It has provided health data for all customer-facing services over 10+ data centers for a statuspage product. Outage is rare.
    \item Developed and maintained a continuous delivery pipeline, using Jenkins and Chef. The applications were packaged into formats such as RPM, wheel, etc. A set of chef recipes is responsible for configuring CentOS, managing system services, setup monitoring agents, etc on bare metals.
    \item Maintained a fleet of AWS resources via Terraform. Inside the VPC, there are a VPC with public and private subnets in 3 availability zones, ALB with security groups attached, NAT gateway, internet gateway, certificates issued by ACM, domain names in Route53, a transit gateway tunneling back to private cloud data centers, etc.
    \item Developed and maintained a Kubernetes cluster using EKS, with EC2 in private subnets as worker nodes. A fleet of applications such as Redis, PostgreSQL, InfluxDB, React Applications run on it. They're managed by Kubernetes YAMLs using resources such as Deployment, DeamonSet, ConfigMap, PVC, Ingress, etc.
    \item Worked with internal operation centers to perform level-1 triage on critical incidents. Built monitoring dashboards and time series queries providing more insights into the production environments.
    \end{rSubsection}

    \begin{rSubsection}{Lipinshuo, Inc}{ May 2015 - September 2016 }{Tech Lead, Software Engineer }{Beijing, China}
    \item Project leadership and management. Capable of leading high performing teams under tough deadlines, to meet expectations of multiple customers externally or internally.
    \item System administration. Maintained configurations for Nginx, supervisord, gunicorn, etc.
    \item System architecture. Developed gateway and message queue applications to improve both the scale and the performance of the entire system.
    \item Continuous Delivery. Wrote packaging tool \href{https://github.com/soasme/beeper.py}{\textit{Beeper}} and deploying tool \href{https://github.com/liwushuo/fapistrano}{\textit{Fapistrano}}.
    \item Migrated image format from JPEG to WEBP. Reduced CDN bandwidth by 75\%.
    \item Developed a fully functional e-shop web application that drove 1k+ orders everyday.
    \item Developed a spider application to scrap production information in other websites.
    \end{rSubsection}

    \begin{rSubsection}{ Douban Read }{ April 2013 - March 2015 }{ Product Development Engineer }{Beijing, China}
    \item Designed and implemented a new version of robust, testable, document-autogen APIs. Reduced network calls by 30\%.
    \item Extracted ORM manipulations with built-in cache mechanism. Reduced model codes by 50\%.
    \item Wrote hundreds of py.test fixtures and thousands of test cases. Improved code coverage by 20\%.
    \item Maintained tens of CI jobs within Jenkins.
    \end{rSubsection}

    \begin{rSubsection}{Douban Book}{ June 2012 - April 2013 }{ Product Development Engineer }{Beijing, China}
    \item Participated on the rebuilding \& refactoring process of \href{book.douban.com}{\textit {Douban Book}}, which was visited by millions of users everyday. Decoupled this system from a monolithic one, to archive independent deployment.
    \item Replaced PTL template engine with Mako.  Reduced codes by tens of thousands of lines.
    \item Implemented a system synchronizing product price and inventory from almost all e-bookshops in China, such as AmazonCN, Jingdong, Dangdang, etc. There were nearly 16 million+ subjects updating everyday.
    \end{rSubsection}

  \end{rSection}

  \iffalse
  \begin{center}
  \textit{ Please refer to \href{http://www.linkedin.com/in/linju}{ my LinkedIn profile } for the complete list of work experience and references.}
  \textit{ http://www.linkedin.com/in/linju }
  \end{center}
  \newpage
  \fi

  \begin{rSection}{Education}
    { \bf Jimei University  } \hfill {\em September 2008 - June 2012 } \\
    { Bachelor Degree in Software Engineering } \\
  \end{rSection}

  \begin{rSection}{Technical Strengths}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
      Computer Languages & Python, JavaScript, Java, C \\
      Protocols & TCP/IP, UDP, HTTP, HTTPS, WSGI \\
      APIs & REST, SOAP, JSON, XML \\
      Databases & MySQL, Postgres, InfluxDB, SQLite, Redis, MongoDB, BeansDB \\
      Infrastructure as Code & Kubernetes, Terraform, Ansible, Chef, Puppet \\
      Python Web Frameworks & Flask, Django, Tornado, Quixote, Celery \\
      Python ORMs & DjangoORM, SQLAlchemy \\
      Python Web Runtimes & Supervisord, Gunicorn, uWSGI, Nginx \\
      Javascript Frameworks & Angular, React \& Redux \\
      VCS & Git, SVN \\
      CIs & Jenkins, TravisCI, CircleCI \\
      Editors & Emacs, Vim, SublimeText, Atom \\
    \end{tabular}
  \end{rSection}

  \begin{rSection}{Open Source Projects}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
      \href{https://github.com/SimpleRegex/SRL-Python}{SRL-Python} & A SimpleRegex implementation in Python. \\
      \href{https://github.com/liwushuo/fapistrano}{fapistrano} & A Python port of Capistrano. \\
      \href{https://github.com/soasme/nim-markdown}{nim-markdown} & A markdown parser implemented in Nim-lang. \\
      \href{https://github.com/soasme/nim-mustache}{nim-mustache} & A mustache template engine implemented in Nim-lang. \\
      \href{https://github.com/soasme/beanstalk-clj}{beanstalk-clj} & A beanstalkd client for language Clojure. \\
    \end{tabular}
  \end{rSection}

\end{document}
